Errata

### 2025-04-07 tex/Manuscript-2.tex
Refactor code structure for improved readability and maintainability

Our results suggest that organic C and N mobilization in water and sediments depends on the interplay of climatic conditions, site characteristics and biocrust presence, in agreement with \citet{Austin2004}. We observed that runoff models captured biocrust effects more accurately than infiltration models, probably because the influence of biocrusts is strongest at the surface and decreases with depth - beyond \SI{7}{\centi\meter} in our study. This observation is consistent with \citet{Williams2022}, who only consider biocrust effects to a depth of about {4}{\centi\meter} in runoff models. This confirms that the presence of surface biocrusts can influence nutrient mobilization in water and sediments \citep{Belnap2003,RodriguezCaballero2013}, not only in arid ecosystems.

@@

\bibliographystyle{natbib} % Consider changing to a style compatible with KOMA/natbib if issues arise
\bibliography{literatur_all_clean}

>>>>

Our results suggest that organic C and N mobilization in water and sediments depends on the interplay of climatic conditions, site characteristics and biocrust presence, in agreement with \citet{Austin2004}. We observed that runoff models captured biocrust effects more accurately than infiltration models, probably because the influence of biocrusts is strongest at the surface and decreases with depth - beyond \SI{7}{\centi\meter} in our study. This observation is consistent with \citet{Williams2022}, who only consider biocrust effects to a depth of about \SI{4}{\centi\meter} in runoff models. This confirms that the presence of surface biocrusts can influence nutrient mobilization in water and sediments \citep{Belnap2003,RodriguezCaballero2013}, not only in arid ecosystems.

@@
